### 2019-09-26 ch7_selfassessment/content.tex
update

Readers are welcome to reuse (and extend) the 110 real and 229 synthetic datasets used in our comparison of TI methods. The datasets are hosted on Zenodo\cite{cannoodt_singlecellomicsdatasets_2018} and the scripts to process them on GitHub\footnote{\href{https://github.com/dynverse/dynbenchmark/tree/master/scripts/01-datasets}{github.com/dynverse/dynbenchmark/tree/master/scripts/01-datasets}}. Note that the ground truths of the datasets are represented using the common data structures format in the previous section.

\section{Multiple metrics}
The largest problem, by far, seems to be a lack of standardised metrics to evaluate TI methods. None of the benchmarks use a metric directly aimed at comparing the topology or pairwise orderings of two trajectories.

@@

While each of these metrics provide some insight the correctness of cell orderings or cell clusterings, they do not evaluate the correctness of the prediction's topology. Using only a pseudotime-based metric to evaluate non-linear trajectories is particularly risky, as it

@@

\section{Further guidelines}

>>>>

Readers are welcome to reuse (and extend) the 110 real and 229 synthetic datasets used in our comparison of TI methods\cite{saelens_comparisonsinglecelltrajectory_2019}. The datasets are hosted on Zenodo\cite{cannoodt_singlecellomicsdatasets_2018} and the scripts to process them on GitHub\footnote{\href{https://github.com/dynverse/dynbenchmark/tree/master/scripts/01-datasets}{github.com/dynverse/dynbenchmark/tree/master/scripts/01-datasets}}. Note that the ground truths of the datasets are represented using the common data structures format in the previous section.

\section{Metrics}
The largest problem, by far, seems to be a lack of standardised metrics to evaluate TI methods. None of the benchmarks use a metric directly aimed at comparing the topology or pairwise orderings of two trajectories.

@@

While each of these metrics provide some insight the correctness of cell orderings or cell clusterings, they do not evaluate the correctness of the prediction's topology. Using only a pseudotime-based metric to evaluate non-linear trajectories is particularly risky, as a \ldots.

@@

\mycomment{explain why.}

Given the multilayered complexity of a trajectory model, it is not trivial to compare the similarity of two trajectory models using only one metric. In Supplementary Note 1 in our comparison of TI methods\cite{saelens_comparisonsinglecelltrajectory_2019}, we describe and illustrate 10 very different metrics for comparing trajectories. We perform a comprehensive characterisation and validation of these metrics on several test cases.

\mycomment{Explain geodesic distance, him, f1 branches, wcor features}
%Its ordering, using the
%371 • Its branch assignment, using the
%372 • Its topology, using the HIM
%373 • The accuracy of differentially expressed features, using the
%374
%F1 branches
%wcor features

\section{Guidelines for benchmarking TI tools}
